Indirect Conflicts: An Exploration and Discussion of Tools, Process, and Developer Insight

### 2013-08-14 iced-2013/paper.tex
ICED skeleton for other research questions now in place.

\section{Results and Discussion}
\label{sec:rnd}

@@

\begin{table*}[tp]
\begin{center}
\begin{tabular}{| p{7cm} | c | c | c | c | c | c | c |}
\hline
Question & Daily & Weekly & Bi-Weekly & Monthly & Bi-Monthly & Yearly & Unknown \\
\hline
\hline
How often do you experience indirect conflicts in your software development? & 17\% & 27\% & 21\% & 17\% & 3\% & 5\% & 10\% \\ \hline
How often do indirect conflicts occur in the early stages of a project’s development? & 32\% & 18\% & 4\% & 5\% & 0\% & 5\% & 36\% \\ \hline
How often do indirect conflicts occur before the first release of a project? & 13\% & 29\% & 6\% & 8\% & 1\% & 3\% & 40\% \\ \hline
How often do indirect conflicts occur after the first release of a project? & 6\% & 18\% & 8\% & 18\% & 1\% & 5\% & 44\% \\ \hline
How often do indirect conflicts occur late in a project’s lifetime? & 6\% & 5\% & 5\% & 18\% & 8\% & 12\% & 46\% \\ \hline
\end{tabular}
\end{center}
\caption{Results of survey questions to how often indirect conflicts occur, in terms of percentage
of developers surveyed.\label{tab:often}}
\end{table*}

@@

>>>>

\section{Results}
\label{sec:rnd}

@@

\begin{table*}[tb!]
\begin{center}
\begin{tabular}{| p{7cm} | c | c | c | c | c | c | c |}
\hline
Question & Daily & Weekly & Bi-Weekly & Monthly & Bi-Monthly & Yearly & Unknown \\
\hline
\hline
How often do you experience indirect conflicts in your software development? & 17\% & 27\% & 21\% & 17\% & 3\% & 5\% & 10\% \\ \hline
How often do indirect conflicts occur in the early stages of a project’s development? & 32\% & 18\% & 4\% & 5\% & 0\% & 5\% & 36\% \\ \hline
How often do indirect conflicts occur before the first release of a project? & 13\% & 29\% & 6\% & 8\% & 1\% & 3\% & 40\% \\ \hline
How often do indirect conflicts occur after the first release of a project? & 6\% & 18\% & 8\% & 18\% & 1\% & 5\% & 44\% \\ \hline
How often do indirect conflicts occur late in a project’s lifetime? & 6\% & 5\% & 5\% & 18\% & 8\% & 12\% & 46\% \\ \hline
\end{tabular}
\end{center}
\caption{Results of survey questions to how often indirect conflicts occur, in terms of percentage
of developers surveyed.\label{tab:often}}
\end{table*}

@@

\begin{description}[topsep=6pt]
	\item[RQ3] \textit{What software artifacts are susceptible to indirect conflicts?}
\end{description}

From the developers interviews, 9 were currently working with large scale database applications and all 9 listed database
schema as a large source of indirect conflicts. Out of the 5 developers interviewed that currently work on either software
library projects or in test, all 5 said that methods or functions were the root of their indirect conflict issues. Some
other notable artifacts were user interface displays for web development, and full components in component base game
architecture.

\subsection{Processes of Indirect Conflicts}

The results that follow pertain to software development process and its relation to indirect conflicts. We explore
how developers react to indirect conflicts, which stakeholders are responsible for their fixes, and if any development
processes can be used to prevent or catch indirect conflicts.

\begin{description}[topsep=6pt]
	\item[RQ4] \textit{How do developers react to and solve indirect conflicts?}
\end{description}

% Here use anything they said for tools and process

\begin{description}[topsep=6pt]
	\item[RQ5] \textit{Who is responsible for fixing indirect conflict issues?}
\end{description}

\begin{description}[topsep=6pt]
	\item[RQ6] \textit{Who is responsible for fixing indirect conflict issues?}
\end{description}

\subsection{Tools for indirect Conflicts}

\begin{description}[topsep=6pt]
	\item[RQ7] \textit{When are pre-emptive indirect conflict tools best used and what would developers want from them?}
\end{description}

\begin{description}[topsep=6pt]
	\item[RQ8] \textit{When are reactionary indirect conflict tools best used and what would developers want from them?}
\end{description}

\section{Discussion}
